\thesistitle

### 2019-07-19 sections/background.tex
Code clone harmfulness

\section{Code clone harmfulness}
There has been a lot of discussion whether code clones should be considered harmful.

Most papers view clones as harmful regarding program maintainability. \textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well. Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work.''} \cite{ostberg2014automatically}

However, the harmfulness of clones depends on a lot of factors. A paper by Kapser et al \cite{kapser2006cloning} describes several patterns of cloning that may not be considered harmful. In this paper Kapser names examples where eliminating clones would compromise other important program qualities. Another study by Jarzabek et al \cite{jarzabek2010clones} categorized ``Essential clones'': clones that are essential because of the solution that is being modelled by the program. Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.

>>>>

\section{Code clone harmfulness}
Although duplication in source code is generally seen as a harmful coding practise that should be avoided. Most papers view clones as harmful regarding program maintainability. \textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well. Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work''} \cite{ostberg2014automatically}. However, in some instances it is undesirable to remove all duplication, as it can lead to unnecessary complexity.

The harmfulness of clones depends on a lot of factors. A paper by Kapser et al \cite{kapser2006cloning} describes several patterns of cloning that may not be considered harmful. In this paper Kapser names examples where eliminating clones would compromise other important program qualities. Another study by Jarzabek et al \cite{jarzabek2010clones} categorized ``Essential clones'': clones that are essential because of the solution that is being modelled by the program. Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.

In this study, one of the main focus points will be to identify what makes a code clone harmful. Analyzing refactoring opportunities of code clones gives an unique insight in the state of the source code in case the duplication is not present. Analyzing these before- and after states of the source code will provide more insights that will help to rank clones based on their harmfulness.
